Marginally-Stable Thermal Equilibria of Rayleigh-Bénard Convection

### 2021-04-21 publication_materials/ms_rbc.tex
Eigentools citation

For various $\Ra$ and fixed $\Pr = 1$, we seek marginally-stable thermal equilibria (MSTE) satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to . 
We employ the \texttt{Dedalus} pseudo-spectral python framework \cite{Dedalus_2020} to solve the EVP outlined in Section \ref{sec:model} as well as the IVP \eq{EQ:T0_IVP} by representing each field with Chebyshev polynomials.
We use the 3/2 dealiasing rule to calculate the advective heat flux.
The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large $\Ra$ admit increasingly small-scale features. 
We use the \texttt{Eigentools} package to manipulate the eigenfunctions and calculate the advective heat flux $\langle w' T' \rangle_x$ \note{cite eigentools}.

>>>>

For various $\Ra$ and fixed $\Pr = 1$, we seek marginally-stable thermal equilibria (MSTE) satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to . 
We employ the \texttt{Dedalus} pseudo-spectral python framework \cite{Dedalus_2020} to solve the EVP outlined in Section \ref{sec:model} as well as the IVP \eq{EQ:T0_IVP} by representing each field with Chebyshev polynomials.
We use the 3/2 dealiasing rule to calculate the advective heat flux.
The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large $\Ra$ admit increasingly small-scale features. 
We use the \texttt{Eigentools} package \cite{Eigentools} to manipulate the eigenfunctions and calculate the advective heat flux $\langle w' T' \rangle_x$.
